---
title: "Technostress Meta-Regressions"
output: html_document
date: '2022-05-13'
---

```{r setup, include=FALSE, echo = F}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(robumeta)
library(metafor)
library(dplyr)
library(downloadthis)

TechnostressData <- read_excel("TechnostressData.xlsx")

MLmodel <- rma.mv(yi = fishers_z, # effect size
                  V = var, # variance
                  random = ~1 | studyID/ESID, # nesting structure, where higher-level variable is                       first and lower-level variable is second (nested)
                  # ~1 indicates the inclusion of a random intercept
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML

summary(MLmodel)

```

## Data Download 

```{r, echo = FALSE}
TechnostressData %>%
  download_this(
    output_name = "Technostress Meta-Analysis Dataset",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "danger",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```

## Meta-Regressions
#### Model below includes all 3 moderators.

```{r, echo = FALSE, warning = FALSE}
regMLmodel <- rma.mv(yi = fishers_z, # effect size
                  V = var, # variance
                  random = ~1 | studyID/ESID, # nesting structure, where higher-level variable is                       first and lower-level variable is second (nested)
                  # ~1 indicates the inclusion of a random intercept
                  mods = ~ pct_fem + dep + avg_age,
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML
summary(regMLmodel)
```

#### Model below includes of percent of sample that are female moderator.
```{r, echo = F, warning = F}
regMLmodel_1 <- rma.mv(yi = fishers_z, # effect size
                  V = var, # variance
                  random = ~1 | studyID/ESID, # nesting structure, where higher-level variable is                       first and lower-level variable is second (nested)
                  # ~1 indicates the inclusion of a random intercept
                  mods = ~ pct_fem,
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML
summary(regMLmodel_1)
```

#### Model below includes depression measure as moderator.
```{r, echo = F, warning = F}
regMLmodel_2 <- rma.mv(yi = fishers_z, # effect size
                  V = var, # variance
                  random = ~1 | studyID/ESID, # nesting structure, where higher-level variable is                       first and lower-level variable is second (nested)
                  # ~1 indicates the inclusion of a random intercept
                  mods = ~ dep,
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML
summary(regMLmodel_2)
```

#### Model below includes of average age of sample moderator.
```{r, echo = F, warning = F}
regMLmodel_3 <- rma.mv(yi = fishers_z, # effect size
                  V = var, # variance
                  random = ~1 | studyID/ESID, # nesting structure, where higher-level variable is                       first and lower-level variable is second (nested)
                  # ~1 indicates the inclusion of a random intercept
                  mods = ~ avg_age,
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML
summary(regMLmodel_3)
```

## Meta-Regression Fit Statistics
#### For model that includes all three moderators.
```{r Meta-Reg Model Fit}
fitstats(regMLmodel) # This should not be compared to the intercept-only MLmodel above because models are not fitted to the same data (missing data for some moderators)
```

|       The test of moderators within the meta-regression model was found to be significant, where $F(3,100) = 5.151, p < .05$. The model fit statistics cannot be directly compared because the same data were not used for both models. Fewer cases were involved in the meta-regression due to missing data pieces where certain studies did not supply the percent of female and average age of participants.

#### Multicollinearity Detection

|       The variance inflation factor (*VIF*) is a measure of multicollinearity (correlation between predictors) that measures how much the variance of the estimated regression coefficients are inflated as compared to when the predictor variables are not linearly related. The below equation to calculate each variable's VIF value estimates the same model coefficient if the other moderator variables in the model had not been included in the model and the corresponding variance.

$\dfrac {Var[b_j]}{Var[b_j^`]} = VIF[b_j]$

<small> Let $b_j$ denote the estimate of the *j*th model coefficient of a particular meta-regression model while $b_j^`$ denotes the same coefficient if the other moderators were not included in the model.</small>

```{r}
vif(regMLmodel, digits = 3)
```

Interpretation:

|       Multicollinearity can adversely impact models because it can increase the variance of the regression coefficients, and create less reliable regression models. The numerical VIF (decimal) value tells you what percentage the variance is inflated for each coefficient.
- e.g. $VIF = 1.1$ indicates the variance for that coefficient is 10% bigger than you'd expect.
- Guidelines to interpret the VIF easily: 
  - $VIF = 1$ = Not correlated
  - $1 < VIF < 5$ = Moderately correlated
  - $VIF >=5$ = Highly correlated

|       All three predictors fit into the moderately correlated category, where `pct_fem` and `avg_age` are the variables with the greatest inflation present. Still, these values are not an immediate cause of concern.

* The variance of percent female of sample moderator is 60.1% bigger than what one would expect if there was no multicollinearity present
* The variance of depression measure moderator is 11.9% bigger than what one would expect if there was no multicollinearity present
* The variance of average age of sample moderator is 74.2% bigger than what one would expect if there was no multicollinearity present

#### Pseudo R-Square

|       The pseudo-$R^2$ is the estimate of the amount of heterogeneity accounted for by the moderators included in the complete meta-regression. computed via the following:

pseudo ${R}^2 = \frac{ {\tau}_{RE}^2-{\tau}_{ME}^2} {{\tau}_{RE}^2}$

|       Where ${\tau}_{RE}^2$ is the total amount of heterogeneity as estimated based on the random-effects (RE) model and ${\tau}_{RE}^2$ is the amount of residual heterogeneity as estimated based on the mixed-effect (ME) model.

|       When including the full set of predictors (`pct_fem`, `avg_age`, and `dep`), the model's psuedo $R^2 = 15.35$, where 15.35% of the variability in the average relationship between technology use and psychological stress can be explained by percent of female participants, the average age of participants, and differentiating between anxiety and depression measures. Because one cannot compute an $R_2$ as one might in OLS regression, the pseudo $R^2 = 15.35$ gives us a rough idea of the predictive power of these moderators.

The psuedo-$R^2$ is also represented via $R^2 = \dfrac {\tau^2_a - \tau^2_b}{\tau^2_a}$ 
where $a$ denotes the compact, intercept-only model and $b$ the full meta-regression model. 

^[López-López, J. A., Marín-Martínez, F., Sánchez-Meca, J., Van den Noortgate, W., & Viechtbauer, W. (2014). Estimation of the predictive power of the model in mixed-effects meta-regression: A simulation study. *British Journal of Mathematical and Statistical Psychology, 67*(1), 30–48.]

```{r}
round(100 * (MLmodel$sigma2[1] - regMLmodel$sigma2[1]) / MLmodel$sigma2[1], 2) # Psuedo-R^2
```


#### Bubble Plots
```{r}
regplot(regMLmodel, mod = "pct_fem", xlab = "Percent Female Participants", refline = 0)
# Bubble plot for pct_female moderator

regplot(regMLmodel, mod = "avg_age", xlab = "Average Age of Participants", refline = 0)
# Bubble plot for avg_age of participants
```
