---
title: "Technostress Publication Bias"
author: "Jay Jeffries"
date: '2022-05-13'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

library(readxl)

TechnostressData <- read_excel("TechnostressData.xlsx")

library(metafor)
library(ggplot2)
library(metaviz)
library(robumeta)
library(ggpubr)
library(pwr)
library(downloadthis)
```

## Data Download 

```{r, echo = FALSE}
TechnostressData %>%
  download_this(
    output_name = "Technostress Meta-Analysis Dataset",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "danger",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```

```{r, echo = FALSE}
SE <- TechnostressData[ ,c("fishers_SE", "fishers_z")]
effectsize <- TechnostressData[ ,"fishers_z"]
effectsize <- TechnostressData[ ,c("fishers_SE", "fishers_z")]

TechStressDat <- abs(TechnostressData[1:127, c(49:51, 9, 56:58)])

sunsetdata <- escalc(measure="ZCOR", ri = fishers_z, ni = N, sei = fishers_SE, vi = var, 
              data = TechStressDat)

res <- rma.uni(yi = TechnostressData$fishers_z, vi = TechnostressData$var, sei = 
          TechnostressData$fishers_SE, method = "HE")

power <-  pwr.r.test(r = TechnostressData$es_Ztocorr, 
                     n = TechStressDat$N,
                     sig.level = 0.05, power = NULL,
                     alternative = "two.sided")

TechnostressData$power <- power$power

base <- robu(formula = fishers_z ~ 1, data = TechnostressData, 
            modelweights = "CORR", studynum = studyID, 
            var.eff.size = var,
            small = TRUE)

base2 <- rma(yi = fishers_z, # effect size
                  vi = var, # variance
                  sei = fishers_SE,
                  test = "t", # use t-tests
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML

```

\newpage
## Publication Bias

### Publication Bias Plots
#### Funnel Plots
```{r}
funnel(base2, refline = .20, main = "Funnel Plot", legend = TRUE)

funnel(base2, level = c(90, 95, 99), 
    shade = c("white", "orange", "red"), main = "Countour-Enhanced Funnel Plot", legend = TRUE)
```

### Power Plots
#### Power and Sunset Plot
```{r}
ggplot(TechnostressData, aes(x = fishers_z, y = power)) +
  geom_point(position = "jitter") +
  labs(x = "Effect Size", y = "Power") + 
  ggtitle("Scatterplot of Average Age and Effect Size by Latent Variable")

viz_sunset(res, contours = TRUE, power_contours =  "continuous")
```

### Publication Bias Tests
#### Egger's Test

```{r Eggers Test}
#robu.egger <- robu(formula = effectsize ~ SE, data = TechnostressData,
#                   modelweights = "CORR", studynum = studyID, 
#                   var.eff.size = var, small = TRUE)
#robu.egger

egger <- regtest(base2, sei = SE, model = "rma")
egger

?regtest()

pub_type_cov <- lm(fishers_z ~ pub_type, data = TechnostressData) %>% summary()
pub_type_cov$r.squared
```

#### Trim and Fill

```{r Trim and Fill}
# Trim and fill standard errors
onelevel <- rma(yi =  fishers_z, sei = fishers_SE, data = TechnostressData)

funnel(onelevel)

trimandfill <- trimfill(onelevel)
# summary(trimandfill2)

funnel(trimandfill, level = c(90, 95, 99),
    shade = c("white", "orange", "red"), main = "Trimmed & Filled Funnel Plot",
    legend = TRUE)
```

#### PET-PEESE

```{r, message = F, warning = F}
#PET <- robu(formula = effectsize ~ SE, data = TechnostressData, 
#              modelweights = "CORR", studynum = studyID, var.eff.size = var)
#print(PET)

PETMod <- rma.uni(yi = fishers_z, # effect size
                  V = var, # variance
                  sei = fishers_SE,
                  data = TechnostressData, # define data
                  method = "REML") # estimate variances using REML
summary(PETMod)

regtest(PETMod, predictor = "sei") # PET Test

PETPlot <- ggplot(TechnostressData) +
  aes(x = fishers_z, y = fishers_SE) +
  geom_point(shape = "circle", size = 1.5, colour = "#196719") +
  geom_smooth(method = "lm", span = 1L) +
  labs(title = "Scatterplot of Fishers z Score and Standard Error") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12L,
    face = "bold",
    hjust = 0.5),
    axis.title.y = element_text(size = 12L,
    face = "bold"),
    axis.title.x = element_text(size = 12L,
    face = "bold")
  )

PETPlot + stat_cor(method = "pearson", label.x = .42, label.y = .097)

se <- seq(0, 0.8, length=100)
funnel(onelevel)
lines(coef(egger$fit)[1] + coef(egger$fit)[2]*se, se, lwd=2) # Using SE for regression line


regtest(PETMod, predictor = "vi") # PEESE Test

PEESEPlot <- ggplot(TechnostressData) +
  aes(x = fishers_z, y = var) +
  geom_point(shape = "circle", size = 1.5, colour = "#196719") +
  geom_smooth(method = "lm", span = 1L) +
  labs(title = "Scatterplot of Fishers z Score and Variance") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12L,
    face = "bold",
    hjust = 0.5),
    axis.title.y = element_text(size = 12L,
    face = "bold"),
    axis.title.x = element_text(size = 12L,
    face = "bold")
  )

PEESEPlot + stat_cor(method = "pearson", label.x = .42, label.y = .0112)

funnel(onelevel)
lines(coef(egger$fit)[1] + coef(egger$fit)[2]*se^2, se, lwd=2) # Using Var for regression line

#fit_PET <- lm(fishers_z ~ fishers_SE, weights = 1/fishers_SE^2, data = TechStressDat)
#summary(fit_PET)$coefficients
#summary(fit_PET)
#confint(fit_PET, 'fishers_SE', level = .95, data = TechStressDat)

# plot(fit_PET)

# variance <- I(TechStressDat$fishers_SE^2)

#fit_PEESE <- lm(fishers_z ~ variance, weights = 1/fishers_SE^2, data = TechStressDat)
#summary(fit_PEESE)$coefficients
#summary(fit_PEESE)
#confint(fit_PEESE, 'variance', level = .95, data = TechStressDat)

```

#### Publication Type Regression

```{r}
lm(data = TechnostressData, fishers_z ~ pub_type) %>% 
  summary()
```

#### Selection Models

```{r, message = F, warning = F}
# library(weightr)

selectionmod <- selmodel(base2, type = "stepfun", steps = c(.025, .05, 1), alternative="two.sided")
summary(selectionmod)
plot(selectionmod, xlim = c(0, .15))
# profile(selectionmod)

# resw <- weightfunct(effect = TechStressDat$fishers_z, v = TechStressDat$var, steps = c(.025, .05), table = TRUE)

#resw

tes(base2)
```
Because this is a two-sided model, the interval 0 < **p** < .025 examines significant values whereas the interval .025 < **p** < .05 examines "marginally" significant, or p-values approaching significance.
