---
title: "Technostress Descriptive Statistics"
author: "Jay Jeffries"
date: "5/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)

# Importing data
#setwd("C:/Users/jjeffries8/OneDrive - University of Nebraska-Lincoln/Desktop/Meta-Analysis")
TechnostressData <- read_excel("TechnostressData.xlsx")

library(dplyr)
library(kableExtra)
library(corrplot)
library(ggplot2)
library(ggpubr)
library(ggridges)
library(expss)
library(geomtextpath)
```

## Data Descriptives 

```{r, echo = FALSE}
TechStressPub = TechnostressData %>% # Creating a new dataset using the origina mtcars dataset       
  # Grouping the dataset by the carb variable
  summarise( 
    "Effect Sizes (ES)" = n(),
    "Published Works" = sum(pub_status == "1"),
    "Unpublished Works" = sum(pub_status == "0"),
    " " = " ",
    "Oldest Publication" = min(pub_year),
    "Newest Publication" = max(pub_year),
    " " = " ",
    "Publication Year" = round(mean(pub_year),0),
    "ES Per Article" = round(mean(ESID, na.rm = TRUE),2)
  )

TechStressSamp = TechnostressData %>% # Creating a new dataset using the origina mtcars dataset       
  # Grouping the dataset by the carb variable
  summarise( 
    "Min. Age" = min(TechnostressData$avg_age, na.rm = TRUE),
    "Max. Age" = max(TechnostressData$avg_age, na.rm = TRUE),
    " " = " ",
    Age = round(mean(avg_age, na.rm = TRUE),2), 
    "Sample Size" = round(mean(N, na.rm = TRUE),2),
    " " = " ",
    Female = round(mean(pct_fem, na.rm = TRUE),2),
    White = round(mean(pct_white, na.rm = TRUE),2),
    Black = round(mean(pct_black, na.rm = TRUE),2),
    Hispanic = round(mean(pct_hispanic, na.rm = TRUE),2),
    Asian = round(mean(pct_asian, na.rm = TRUE),2),
    Native = round(mean(pct_native, na.rm = TRUE),2),
    "Multiple Race/Ethnicity" = round(mean(pct_multi, na.rm = TRUE),2)
)

TechStressDesc = TechnostressData %>% # Creating a new dataset using the origina mtcars dataset       
  # Grouping the dataset by the carb variable
  summarise( 
    "Anxiety ES" = sum(TechnostressData$anx, na.rm = TRUE),
    "Depression ES" = sum(TechnostressData$dep, na.rm = TRUE),
    "K-12 Ed. Samples" = sum(TechnostressData$K12, na.rm = TRUE),
    "Higher Ed. Samples" = sum(TechnostressData$higher, na.rm = TRUE),
    " " = " ",
    "Min. ES" = min(es_Ztocorr),
    "Max. ES" = max(es_Ztocorr),
    "Unweighted ES" = round(mean(es_Ztocorr, na.rm = TRUE),2) # changing the (,2) will round the average to whatever number of decimal points you would prefer
  )
```

```{r PubDescriptives, echo = FALSE}
PubDescriptives <- kbl(TechStressPub, caption = "Table 1. Publications Descriptive Statistics") %>%
  add_header_above(c("Frequency (N)" = 3, " " = 1, "Range" = 2 , "Mean Statistic" = 2)) %>%
  row_spec(0, bold = TRUE) %>%
  kable_paper("hover", font_size = 12, full_width = TRUE) %>%
  kable_styling(html_font = "serif")
PubDescriptives
```
**Figure 1. Correlation Matrix of Publication Characeristics**
```{r PubCorr, echo = FALSE}
vars4 <- TechnostressData %>% select(fishers_z, pub_year, pub_status, pub_type, N)
corrvar4 <- cor(vars4, use = "pairwise.complete.obs")
corrvar4[lower.tri(corrvar4, diag = TRUE)] <- NA
corrplot(corrvar4, method = "number", type = "upper", diag = FALSE)
```

- Articles ranged from 2012 to 2021, which shows my meta-analysis utilizes information within 9 years of relevant data.
- Of the 127 effect sizes, 10 derived from unpublished works. 
- These articles (published and unpublished) range from 2012 to 2021, where the average year is 2018.
- The mean number of effect sizes drawn from these works $\approx$ 3.

```{r SampleDescriptives, error = FALSE, message = FALSE, warning = FALSE, echo = FALSE}
SampleDescriptives <- kbl(TechStressSamp, caption = "Table 2. Sample Descriptive Statistics") %>%
  add_header_above(c(" " = 5, "% of Sample" = 7)) %>%
  add_header_above(c("Range" = 2, " " = 1, "Mean Statistic" = 9)) %>%
  row_spec(0, bold = TRUE) %>%
  kable_paper("hover", font_size = 12, full_width = TRUE) %>%
  kable_styling(html_font = "serif")
SampleDescriptives
```

**Figure 2. Correlation Matrix of Sample Characteristics**

```{r SampleDescripPlots, echo = F, message = F}
vars2 <- TechnostressData %>% select(fishers_z, pct_fem, pct_black, pct_hispanic, pct_asian, pct_native, pct_multi, pct_white)
corrvar2 <- cor(vars2, use = "pairwise.complete.obs")
corrvar2[lower.tri(corrvar2, diag = TRUE)] <- NA
corrplot(corrvar2, method = "number", type = "upper", diag = FALSE)

ggplot(TechnostressData, aes(x = es_Ztocorr)) +
  geom_histogram(aes(y=..density..), alpha=0.5, 
  position="identity") +
  geom_density(alpha=.2) +
  labs(title = "Figure 3. Histogram of Fishers z Scores",
      x = "Pearson Correlation Coefficient", y = "Frequency", 
      caption = "Note: Fishers z scores were converted into Pearson product-moment correlation coefficients for full interpretation.")
```

- Participant's age ranged from 11.2 to 24.4 years, where the mean years of age was 17.2. 
- The average number of participants per sample ($N$) $\approx$ 4316 participants.

```{r StudyDescriptivesTable, echo = FALSE}
StudyDescriptives <- kbl(TechStressDesc, caption = "Table 3. Study Descriptive Statistics") %>%
  add_header_above(c("Frequency (N)" = 4, " " = 1, "Range" = 2, "Average Statistic" = 1)) %>%
  row_spec(0, bold = TRUE) %>%
  kable_paper("hover", font_size = 12, full_width = TRUE) %>%
  kable_styling(html_font = "serif")
StudyDescriptives
```
- The effect sizes were separated by the type of latent (unobservable) variable being measured.
  - The number of relationships between technology use and anxiety = 54.
  - The number of relationships between technology use and depression = 70.
  - The remaining effect sizes were either a measure of fatigue, a combination of anxiety *and* depression, a combination of depression *and* fatigue, or a combination of anxiety *and* fatigue.
- Of those that reported the settings for observations, 64 derive from K-12 classrooms and 53 from post-secondary contexts. 

**Figure 4. Correlation Matrix of Study Characteristics**

```{r SampleCorr, echo = FALSE}
vars1 <- TechnostressData %>% select(fishers_z, avg_age, K12, higher, dep, anx)
corrvar1 <- cor(vars1, use = "pairwise.complete.obs")
corrvar1[lower.tri(corrvar1, diag = TRUE)] <- NA
corrplot(corrvar1, method = "number", type = "upper", diag = FALSE)
```
- Effect sizes, or Pearson product-moment correlation coefficients ranged from $r = -.25$ to $r =.58$. The average unweighted association between measure of psychological well being and technology use is small to moderate ($r = .23$).

```{r, include = FALSE, warnings = FALSE, errors = FALSE, message = FALSE}
# The reliability estimates of anxiety, depression, fatigue, or FOMO measurements range from a Cronbach's alpha of 0.73 to 0.96.
range(TechnostressData$reliability, na.rm = TRUE)
```

\newpage

## Exploratory Data Analysis {#Exploratory-Data-Analysis}
### Figures & Plots
Building a case for why each moderator is included

```{r ridgelines, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}
ggplot(TechnostressData, aes(x = es_Ztocorr, y = school_type, fill = school_type)) +
  stat_density_ridges(quantile_lines = TRUE, quantiles = 2) +
  ggtitle("Effect Size Density by School Type") +
  labs(x = "Effect Size", y = "School Type", caption = "0 = Primary/Secondary, 1 = Higher, NA = Undefined") +
  theme_minimal() 

ggplot(TechnostressData, aes(x = es_Ztocorr, y = school_type, fill = school_type)) +
  geom_density_ridges(
   jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
    vline_size = 1, vline_color = "red",
    point_size = 0.4, point_alpha = 1,
    position = position_raincloud(adjust_vlines = TRUE)) +
  ggtitle("Effect Size Density by School Type") +
  labs(x = "Effect Size", y = "School Type", caption = "0 = Primary/Secondary, 1 = Higher, NA = Undefined") +
  theme_minimal()

ggplot(data = subset(TechnostressData, !is.na(latent_var)), 
       aes(x = es_Ztocorr, y = dep, fill = latent_var)) +
  stat_density_ridges(quantile_lines = TRUE, quantiles = 2,  na.rm = TRUE) +
  ggtitle("Correlation Coefficient Density by Psychological Wellbeing Variable") +
  labs(x = "Effect Size", y = "Psychologoical Symptom") +
  scale_y_continuous(labels = c("Anxiety", "Depression"), breaks = c(0, 1), limits = c(0, 2.85)) +
  theme_minimal() +
  theme(legend.position = "none")

ggplot(data = subset(TechnostressData, !is.na(latent_var)), 
       aes(x = es_Ztocorr, y = dep, fill = latent_var, color = dep)) +
  geom_density_ridges(
   jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
    vline_size = 1, vline_color = "red",
    point_size = 0.4, point_alpha = 1,
    position = position_raincloud(adjust_vlines = TRUE)) +
  ggtitle("Effect Size Density by Psychological Stress Variable") +
  labs(x = "Effect Size", y = "Psychological Symptom") +
  scale_y_continuous(labels = c("Anxiety", "Depression"), breaks = c(0, 1), limits = c(-.5, 2)) +
  theme_minimal() +
  theme(legend.position = "none")

val_lab(TechnostressData$school_type) = num_lab("
0 Primary/Secondary
1 Higher
")

val_lab(TechnostressData$latent_var) = num_lab("
0 Anxiety
1 Depression
")

#ggplot(TechnostressData, aes(x = es_Ztocorr, color = school_type)) +
#  geom_textpath(aes(label = school_type), stat = "density",
#                size = 4, fontface = 4, hjust = 0.2, vjust = 0.3) +
#  theme_minimal() +
#  theme(legend.position = "none")

ggplot(TechnostressData, aes(x = es_Ztocorr, color = latent_var)) +
  ggtitle("Correlation Density Plots by Depression and Anxiety Symptoms") + 
  labs(x = "Correlation Coefficient", y = "Frequency", caption = "Green line indicates average weighted Pearson product-moment correlation") +
  geom_vline(aes(xintercept = .2025), color = "forestgreen", size = .8) +
  geom_textpath(aes(label = latent_var), stat = "density",
                size = 4, fontface = 4, hjust = 0.2, vjust = 0.3) +
  theme_minimal() +
  theme(legend.position = "none")

aa <- ggplot(TechnostressData, aes(x = es_Ztocorr, y = avg_age)) +
  geom_point(position = "jitter") +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  labs(x = "Correlation Coefficient", y = "Average Age") + 
  ggtitle("Scatterplot of Correlation and Average Age of Participants") + 
  theme_minimal()

aa + stat_cor(method = "pearson", label.x = .41, label.y = 23)

pf <- ggplot(TechnostressData, aes(x = es_Ztocorr, y = pct_fem)) +
  geom_point(position = "jitter") +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  labs(x = "Correlation Coefficient", y = "% Female Participants") + 
  ggtitle("Scatterplot of Correlation and Percentage of Female Participants") + 
  theme_minimal()

pf + stat_cor(method = "pearson", label.x = .42, label.y = 77)

```

## Missing Covariate Data
### Percent Missing Values for Moderators

```{r}
age_summary <- summary(TechnostressData$avg_age)
fem_summary <- summary(TechnostressData$pct_fem)

# Average Age of Participant Missingness
age_summary[[7]] / nrow(TechnostressData)

# Percent Female of Sample Missingness
fem_summary[[7]] / nrow(TechnostressData)
```

```{r, echo = F, eval = F, warnings = FALSE, errors = FALSE, message = FALSE}
ggscatter(TechnostressData, x = "fishers_z", y = "avg_age",
  facet.by  = "school_type", 
  short.panel.labs = FALSE) +
  stat_smooth(method = "loess", span = 0.9)
# Generally speaking, it appears that the older you are, the smaller the effect size across all three school types. 

ggplot(TechnostressData, aes(x = fishers_z, y = avg_age, col = school_type, fill = school_type)) + 
  geom_point(position = "jitter") +
  geom_textsmooth(aes(label = school_type, color = school_type), 
                  method = "lm", formula = y ~ x, size = 4, linetype = 3, 
                  fontface = 3, linewidth = 1, vjust = -0.5,) +
  labs(x = "Effect Size", y = "Average Age") + 
  stat_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "#1b9e77") +
  ggtitle("Scatterplot of Average Age and Effect Size by School Type") +
  stat_ellipse(geom = "polygon", aes(fill = school_type), 
                      alpha = 0.2,
                      level = 0.95) + 
  theme(legend.position = "none")

# A strong, negative correlation between average age and effect size exists, r = -0.603. There is the greatest amount of variance in effect sizes from studies that regard higher education (school_type = 3) than secondary (school_type = 2) or primary (school_type = 1). 

ggscatter(TechnostressData, x = "fishers_z", y = "avg_age",
  facet.by  = "latent_var", 
  short.panel.labs = FALSE) +
  stat_smooth(method = "loess", span = 0.9)
# It appears that the latent variable anxiety has a slightly curvilinear relationship with average age. This shows that, for those studies that involved average ages between ~15-20, effect sizes were generally larger than other age groups.  

ggplot(TechnostressData, aes(x = fishers_z, y = avg_age, color = latent_var, fill = latent_var)) +
  geom_point(position = "jitter") +
  labs(x = "Effect Size", y = "Average Age") + 
   geom_textsmooth(aes(label = latent_var, color = latent_var), 
                  method = "lm", formula = y ~ x, size = 4, linetype = 3, 
                  fontface = 3, linewidth = 1, vjust = -0.5, color = "orange") +
  ggtitle("Scatterplot of Average Age and Effect Size by Latent Variable") +
  stat_ellipse(geom="polygon", aes(fill = latent_var), 
                      alpha = 0.2,
                      level = 0.95) + 
  theme(legend.position = "none")

# A negative relationsihp exists between age and size of effect. In addition, there is greater variability in the size of effect for studies regarding anxiety (latent_var = 0) than depression (1) or fatigue (2). 

ggscatter(TechnostressData, x = "fishers_z", y = "pct_fem",
  facet.by  = "latent_var", 
  short.panel.labs = FALSE) +
  stat_smooth(method = "loess", span = 0.9)
# Interestingly, studies with a greater percent of female students using technology found there to be lower effects when in the secondary school type. Note--there are about equal % of male and female participants when effect sizes are largest, indicating that technology use with a homogenously female sample COULD lead to less indication of technostress effects. 

# In general, the higher % of females in the sample for higher education, the larger the effects. This relationship is not strong, where

ggscatter(TechnostressData, x = "fishers_z", y = "pct_fem",
  facet.by  = "school_type", 
  short.panel.labs = FALSE) +
  stat_smooth(method = "loess", span = 0.9)

ggplot(TechnostressData, aes(x = fishers_z, y = pct_fem, color = school_type, fill = school_type)) + 
  geom_point(position = "jitter") +
  labs(x = "Effect Size", y = "Percent Female") + 
  geom_textsmooth(aes(label = school_type, color = school_type),
                  method = "lm", formula = y ~ x, 
  se = FALSE) +
  ggtitle("Scatterplot of Percent of Female Participants and Effect Size")
# A moderate, negative association between percent female and effect size is found in the data r = -0.229. 

ggplot(TechnostressData, aes(x = fishers_z, y = pct_black)) + 
  geom_point(position = "jitter") +
  labs(x = "Effect Size", y = "Percent Black or African American Participants") + 
  geom_smooth(method = "lm", formula = y ~ x, 
  se = FALSE, color = "#1b9e77") +
  ggtitle("Scatterplot of Frequency Black Participants Moderator and Effect Size")
cor(TechnostressData$fishers_z, TechnostressData$pct_black, use = "complete.obs")
# There is a moderate, negative relationships between the effect size and percent of Black or African American participants, r = -0.322. 

ggplot(TechnostressData, aes(x = fishers_z, y = pct_white)) + 
  geom_point(position = "jitter") +
  labs(x = "Effect Size", y = "Percent White Participants") + 
  geom_smooth(method = "lm", formula = y ~ x, 
  se = FALSE, color = "#1b9e77") +
  ggtitle("Scatterplot of Frequency White Participants Moderator and Effect Size")
cor(TechnostressData$fishers_z, TechnostressData$pct_white, use = "complete.obs")
# There is a moderate, negative relationships between the effect size and percent of Black or African American participants, r = -0.346. 
```
